The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-11-25 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}, \]
where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
%It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
%As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
Following our outline, we define
\[ \ft^{\idealm}(f) \coloneqq  \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]

>>>>

For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
Given an ideal $I$ of a ring $R$ of characteristic $p>0$, $I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$. If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, the limit of $\frac{\lambda\left(R/I^{[p^e]}\right)}{p^{ed}}$ is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.

Consider a nonzero polynomial $f$ and a natural number $e$.  If $f$ does not vanish at the origin, then set $\nu_f^{\idealm}(p^e) := \infty$.  Otherwise, $f \in \idealm$, and we instead define
\[ \nu_f^{\idealm}(p^e) \coloneqq  \max \{ n \in \mathbb{N} : f^n \notin \idealm^{[p^e]} \}. \]
%where $\idealm^{[p^e]}$ denotes the $p^e$-th Frobenius power of $\idealm$, that is, the ideal generated by the $p^e$-th powers of the elements of $\idealm$.
%It is not hard to see that this number is the largest power of $f$ that is part of a free basis for the localization of the ambient polynomial ring at the origin, over its subring of $p^e$-th powers.
%As noted earlier, this number also has a natural interpretation in terms of $F$-purity of pairs.
Following our outline, we define
\[ \ft^{\idealm}(f) \coloneqq  \lim_{e \to \infty} \frac{ \nu_f^{\idealm}(p^e)}{p^e}. \]
